\texttt{\texttt{NeuralNetworkVisualization}}

### 2019-09-23 paper_neural_network.Rmd
Final Version of paper!

---
title: \texttt{\texttt{NeuralNetworkVisualization}}
subtitle: \LARGE{A dynamic approach with R shiny} 
author: 
- \Large{\textbf{\emph{Alex Afanasev and Jacqueline Seufert}}}
- 'Advanced Statistical Programming with R'
- 'M.Sc. Applied Statistics'
- 'Georg-August-University Göttingen'
date: \today
header-includes:
- \usepackage{titling}
- \usepackage{placeins}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \onehalfspacing
- \setlength{\droptitle}{10em} 
output:
  pdf_document:
      number_sections: true
      fig_caption: yes
bibliography: bibneural.bib

@@

Let us consider the partial dependence plots with bootstrap confidence intervals to capture the uncertainty of the effect. The thick line with points represents the average partial dependence and the thiner lines around it the lower as well as the upper bound from the confidence interval. We can use the stored data to create the partial dependence plot with the \texttt{probs} and \texttt{nrepetitions} parameters specified as in the \texttt{options} parameter where the model has been fitted.

@@

We hereby declare that we have produced this work independently and without outside assistance, and have used only the sources and tools stated. We have clearly identified the sources of any sections from other works that we have quoted or given in essence. We have complied with the guidelines on good academic practice at the University of Göttingen. If a digital version has been submitted, it is identical to the written one. we are aware that failure to comply with these principles will result in the examination being graded “nicht bestanden”, i.e. failed.

\bigskip
\bigskip
Göttingen, 18th September 2019\

\bigskip
\bigskip
Alex Afanasev\

\bigskip
\bigskip
Jacqueline Dorothea Seufert\
\newpage

>>>>

---
title: \texttt{\texttt{NeuralNetworkVisualization}}
subtitle: \LARGE{A dynamic approach with R shiny} 
author: 
- \Large{\textbf{\emph{Alex Afanasev and Jacqueline Seufert}}}
- 'Advanced Statistical Programming with R'
- 'M.Sc. Applied Statistics'
- 'Georg-August-University G&ouml;ttingen'
date: \today
header-includes:
- \usepackage{titling}
- \usepackage{placeins}
- \usepackage{setspace}
- \usepackage{chngcntr}
- \onehalfspacing
- \setlength{\droptitle}{10em} 
output:
  pdf_document:
      number_sections: true
      fig_caption: yes
bibliography: bibneural.bib

@@

Let us consider the partial dependence plots with bootstrap confidence intervals to capture the uncertainty of the effect. The thick line with points represents the average partial dependence and the thinner lines around it the lower as well as the upper bound from the confidence interval. We can use the stored data to create the partial dependence plot with the \texttt{probs} and \texttt{nrepetitions} parameters specified as in the \texttt{options} parameter where the model has been fitted.

@@

We hereby declare that we have produced this work independently and without outside assistance, and have used only the sources and tools stated. We have clearly identified the sources of any sections from other works that we have quoted or given in essence. We have complied with the guidelines on good academic practice at the University of G&ouml;ttingen. If a digital version has been submitted, it is identical to the written one. we are aware that failure to comply with these principles will result in the examination being graded \"nicht bestanden\", i.e. failed.

\bigskip
\bigskip
G&ouml;ttingen, 18th September 2019

\bigskip
\bigskip
Alex Afanasev

\bigskip
\bigskip
Jacqueline Dorothea Seufert
\newpage
